The \project{unRAVE} catalog

### 2016-08-17 article/unrave.tex
minor

\title{The \project{unRAVE} catalog of X.X million detailed stellar abundances for chemodynamic studies}

@@

The first \project{Gaia} data release will include positions, proper motions, and 
parallaxes for approximately two million stars in the Tycho-2 \citep{Hog_2000} 
catalog \citep{Michalik_2015a,Michalik_2015b}.  After cross-matching all major 
stellar spectroscopic surveys\footnote{Specifically we cross-matched the Tycho-2
catalog against the \project{APOGEE} \citep{Zasowski_2013}, \project{GALAH} 
\citep{DeSilva_2015}, \project{Gaia-ESO} \citep{Gilmore_2012,Randich_2013}, 
\project{LAMOST} \citep{Cui_2012}, and \project{RAVE} \citep{Steinmetz_2006} 
surveys}, we found the RAdial Velocity Experiment (hereafter \rave) survey to 
have the largest overlap with the first \project{Gaia} data release: 292,036 
stars.  We then used the \project{Gaia} universe model \citep{Robin_2012} to 
estimate the precision in parallax and proper motions that will be available in 
\project{Gaia} DR1 for every star in these cross-matches.  Comparing the expected
precision to what is currently available, we further found that the \project{RAVE}
survey will benefit most from \project{Gaia} DR1.  The distances of 63\% of the 
\project{RAVE}--\project{Gaia} DR1 overlap sample (182,862 stars) are expected to
improve with the first \project{Gaia} data release, and 47\% of stars likely to
have better proper motions (137,211 stars).  This motivated us to examine what 
chemical abundance information was available for \rave, and to evaluate whether 
we could enable new chemodynamic studies by contributing to this existing set of
chemical abundances.

@@

>>>>

\title{The \project{unRAVE} catalog}

@@

The first \project{Gaia} data release will include positions, proper motions, and 
parallaxes for approximately two million stars in the Tycho-2 \citep{Hog_2000} 
catalog \citep{Michalik_2015a,Michalik_2015b}.  After cross-matching all major 
stellar spectroscopic surveys\footnote{Specifically we cross-matched the Tycho-2
catalog against the \project{APOGEE} \citep{Zasowski_2013}, \project{Gaia-ESO} 
\citep{Gilmore_2012,Randich_2013}, \project{GALAH} \citep{DeSilva_2015},
\project{LAMOST} \citep{Cui_2012}, and \project{RAVE} \citep{Steinmetz_2006} 
surveys}, we found the RAdial Velocity Experiment (hereafter \rave) survey to 
have the largest overlap with the first \project{Gaia} data release: 292,036 
stars.  We then used the \project{Gaia} universe model \citep{Robin_2012} to 
estimate the precision in parallax and proper motions that will be available in 
\project{Gaia} DR1 for every star in these cross-matches.  Comparing the expected
precision to what is currently available, we further found that the \project{RAVE}
survey will benefit most from \project{Gaia} DR1.  The distances of 63\% of the 
\project{RAVE}--\project{Gaia} DR1 overlap sample (182,862 stars) are expected to
improve with the first \project{Gaia} data release, and 47\% of stars likely to
have better proper motions (137,211 stars).  This motivated us to examine what 
chemical abundance information was available for \rave, and to evaluate whether 
we could enable new chemodynamic studies by contributing to this existing set of
chemical abundances.

@@

\section{Discussion}
\label{sec:discussion}
